Index measures for oak decline severity using phenotypic descriptors

### 2019-12-13 manuscript/manuscript.Rmd
added to methods section

@@

To account for these differences and to make the trees across the sites comparable in the context of decline, an adjustment of site means to the overall mean was applied to each of the size descriptors (diameter at breast height, lower crown height, timber height, total height, crown radius). 
An example of this adjustment is shown for diameter at breast height in Supplementary Figure # and the adjustment factors for each of the descriptors at each site is shown in Supplementary Table #.

@@

### Overall and local descriptor importance

- LIME analysis to identify locally important descriptors under circumstances of interest
- simulated descriptor response surfaces

Individual random forest regression models of the phenotypic descriptors were trained, supervised using each decline index.
Optimal number of trees (ntree) and number randomly of variables (mtry) parameters for random forest were tuned prior to training. 
The combination parameters giving the lowest percent mean absolute error (PMAE) were selected and as follows: PDI - `r glue('ntree = {PDI_rf_tune_params$ntree}, mtry = {PDI_rf_tune_params$mtry}, PMAE = {PDI_rf_tune_params$PMAE %>% signif(digits = 3)}%')`; DAI - `r glue('ntree = {DAI_rf_tune_params$ntree}, mtry = {DAI_rf_tune_params$mtry}, PMAE = {DAI_rf_tune_params$PMAE %>% signif(digits = 3)}%')` (Supplementary figure #)

To understand the descriptors contributing to each of the indexes, Local Interpretable Model-Agnostic Explanations (LIME) using the lime R package v`r packageVersion('lime') %>% as.character()` [@ribeiro2016; @pedersen2019]

@@

### Descriptor contributions and trends

>>>>

To account age, size and site specific tree difference, an adjustment of site means to the overall mean was applied to each of the size descriptors (diameter at breast height, lower crown height, timber height, total height, crown radius). 
An example of this adjustment is shown for diameter at breast height in Supplementary Figure # and the adjustment factors for each of the descriptors at each site is shown in Supplementary Table #.

@@

@@

### Identifying important descriptors and their trends within the decline indexes

- simulated descriptor response surfaces

Individual random forest regression models of the phenotypic descriptors were trained, supervised using each decline index.
The optimal number of trees (ntree) and number randomly of variables (mtry) parameters for random forest were tuned prior to training. 
The combination parameters giving the lowest percent mean absolute error (PMAE) were selected and set as follows: PDI - `r glue('ntree = {PDI_rf_tune_params$ntree}, mtry = {PDI_rf_tune_params$mtry}, PMAE = {PDI_rf_tune_params$PMAE %>% signif(digits = 3)}%')`; DAI - `r glue('ntree = {DAI_rf_tune_params$ntree}, mtry = {DAI_rf_tune_params$mtry}, PMAE = {DAI_rf_tune_params$PMAE %>% signif(digits = 3)}%')` (Supplementary figure #)

Local Interpretable Model-Agnostic Explanations (LIME) To understand the descriptors contributing to case specific examples of each of the indexes,  were computed for a range of specific cases [@ribeiro2016]. 
The lime R package v`r packageVersion('lime') %>% as.character()` was used with the default parameters [@pedersen2019].
A low, a moderate and a severe decline cases was used for the PDI. For each case, a tree with a score closest to 0, 0.5 and 1 respectively was selected.
For the DAI, a decline neautral case was selected with a score closes to 0.
Then for each of the AOD and COD syndrome types a moderatefor the DAI .

@@

### Descriptor contributions and trends to the decline indexes
